### 2021-04-21 SupplementaryMaterial/Vita.tex
Updates from Overleaf

\item Shuai Wang, Wenhao Wang, \textbf{Qinkun Bao}, Pei Wang, Xiaofeng Wang, and Dinghao Wu, ``Binary Code Retrofitting and Hardening Using SGX'', in \emph{Proceedings of the 2017 workshop on Forming an Ecosystem Around Software Transformation (FEAST17)}, co-located with CCS 2017, Dallas, USA, November 3, 2017
\end{enumerate}

>>>>

\item Shuai Wang, Wenhao Wang, \textbf{Qinkun Bao}, Pei Wang, Xiaofeng Wang, and Dinghao Wu, ``Binary Code Retrofitting and Hardening Using SGX'', in \emph{Proceedings of the 2017 workshop on Forming an Ecosystem Around Software Transformation (FEAST17)}, co-located with CCS 2017, Dallas, USA, November 3, 2017

\item Shilin Zhu, Siyao Meng, \textbf{Qinkun Bao}, Xiaoliang Chen, and Zuqing Zhu, ``Availability-Aware Service Provisioning in EONs: How Efficient will FIPP-p-Cycles be?",  in \emph{Proceedings of IEEE/OSA Optical Fiber Communication Conference (OFC)}, paper W2A.51, March 2016

\item Xiaoliang Chen, Fan Ji, Shilin Zhu, \textbf{Qinkun Bao}, and Zuqing Zhu, ``Availability-Aware Service Provisioning in SD-EON based Inter-Datacenter Networks",  \emph{Photonic Network Communications (Springer)}, vol. 31, no. 3, pp. 543-549, June 2016
\end{enumerate}
